---
output: rmarkdown::github_document
---

# blackmagic

Automagically Convert XML to JSON

## Description

Given a character string of 'XML', an 'xml2' or 'XML' package document,
or a 'URL' to retrieve XML content from, convert said 'XML' to 'JSON' using 
the 'xml-js' 'npm' library <https://www.npmjs.com/package/xml-js> by Yousuf Almarzooqi.
    
## NOTE

Please reconsider your apparent desire to use this package.

Automagic conversion of XML to JSON is _rarely_ a good idea and a path fraught with peril. There are _so many_ options to tweak to ensure you get what you think you want but likely truly want something else entirely, such as a more minimal extract of the original XML file.

Seriously consider parsing the XML then using `purrr` idioms to extract the data you need into a proper `list` and _then_ call `jsonlite::toJSON()` on said `list`.

## What's Inside The Tin

The following functions are implemented:

- `xml_to_json`:	Convert XML to JSON

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/blackmagic")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(blackmagic)

# current verison
packageVersion("blackmagic")

```

### Sample (defaults)

```{r}

xml <- '<?xml version="1.0" encoding="utf-8"?>
<note importance="high" logged="true">
    <title>Happy</title>
    <todo>Work</todo>
    <todo>Play</todo>
</note>'

cat(xml_to_json(xml))
```

### Sample (`xml2`)

```{r}
cat(xml_to_json(xml2::read_xml(xml)))
```

### Sample (`XML`)

```{r}
cat(xml_to_json(XML::xmlParse(xml)))
```

### Sample (URL + saner tweaks)

```{r}
cat(xml_to_json("https://httpbin.org/xml", spaces = 2, compact = FALSE, ignoreDeclaration = TRUE))
```

### Sample (some saner tweaks)

```{r}
'<?xml version="1.0" encoding="UTF-8"?>
<bookstore>
  <book category="cooking">
    <title lang="en">Everyday Italian</title>
    <author>Giada De Laurentiis</author>
    <year>2005</year>
    <price>30.00</price>
  </book>
  <book category="children">
    <title lang="en">Harry Potter</title>
    <author>J K. Rowling</author>
    <year>2005</year>
    <price>29.99</price>
  </book>
  <book category="web">
    <title lang="en">Learning XML</title>
    <author>Erik T. Ray</author>
    <year>2003</year>
    <price>39.95</price>
  </book>
</bookstore>' -> books

cat(xml_to_json(books, spaces = 2, compact = TRUE, ignoreDeclaration = TRUE))
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.